Turbulence in compact to giant HII regions

### 2021-07-30 mnras_template.tex
Will change - not sure what

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  We apply the technique to archival \halpha\ observations of a diverse sample of 8 \hii{} regions
  in the Milky Way and other Local Group galaxies,
  which span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form to the second-order velocity structure function,
  we extract three parameters for the fluctuations in each region:
  total velocity dispersion, \(\sigma\),
  autocorrelation length, \(r_0\), and power-law slope, \(m\).
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

@@

\section{Introduction}

@@

The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
\begin{tabular}{ccccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

\subsection{Regions in M33 galaxy and NGC 6822}

@@

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}.

@@

where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise.

The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data. 
In this way we avoid one fundamental problem in the interpretation of the structure function results. The slope in the majority of previous studies and hence, the correlation length, is obtained by eye. 
The canonical way to find it is to determine a particular range of ascending values in the structure function results. 
If this increase in values is reversed it is commonly assumed that one particular range has been found. 
In some cases this procedure keeps going up to large scales, having two or more inertial regimes giving as a interpretation multiple energy injection scales.
Since the results using the canonical method aren't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results.
This way we can maintain consistency in our analysis of multiple regions and keep the possibility open to enhance our sample with future consistency.

@@

\begin{table*}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..347H}
      g) \citet{arthur2016turbulence}.
    } 
\begin{tabular}{cccccc}\hline
HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
30Dor     & 265.56*  &    252.79           &    363 059    &0.2&   c    \\
Carina    & -8.83    &    17.89         &   855    &&   d    \\
NGC 346   &          &       31.36           &    112 796   &&       \\
Lagoon    & -6.26 &    7.53    &    1 176    &&   e   \\
Orion Large     &     -1.25    &     10.43    &    359    &&    f   \\
Orion Small     &         &        &        &&    g   \\
\end{tabular}\label{tab:Data}
\end{center}
\end{table*}

@@

Table \ref{tab:Res} presents the main parameters we obtain from the analysis on the fluctuations of the velocities.
The first column is the velocity dispersion, \(\sigma\), of each sample of centroid velocities.
The second column is the correlation length, \(r_0\).
The third column is the index \(m\) that is used to fit our results.
This index is used as a reference for comparison between theory and observations.
In the forth column we show the separation where the value 2\(\sigma\) is reached.
We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box.
With the aim to investigate how statistically homogeneous the regions are, we also show the value of $\sigma_{LOS}$.

The final column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as \citet{1987A&A...176..347H}

@@

where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation. It is possible to calculate how this Taylor micro-scale is related to the correlation length by:

@@

%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.
The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc.
The structure functions keep going up to scales of 70 pc following a periodic pattern.
In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.
The structure functions for NGC 604, follow a periodic behavior around 2$\sigma$.
We can think of a wave starting around 30 pc, with a series of $ >$2$\sigma$ values up to $\sim$100 pc.
Then $<$2$\sigma$ values follow until the scales of 150 pc.
Therefore we relate periodic behavior to scales of magnitude $\sim$100 pc across our sample box.
For NGC 595 the values obtained are 1.75 and 9 pc.
The structure function goes up until 30 pc, reaching values above 2$\sigma$ before falling.

For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
Both regions reach a maximum of 2$\sigma$ around 20 pc.
The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and and index of 1.22.
NGC 346 has a correlation length of 1.4 and an index of 1.13.

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}.
Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results.
Carina has an index of 1 with a correlation length of 0.55 pc.
The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc.

The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.378 pc and a index of 1.13.
For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc.
For scales greater than 6 pc large-scale correlation is found up to 15 pc.

For Orion (M42) we have the opportunity to study two different observations with different implications. \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc. Large scales results shows an index of 0.84 with a correlation length of 0.9 pc while the small scales have 1.44 and 0.062 pc.

\begin{table*}
\begin{center}\caption{Main results.}
\begin{tabular}{cccccccccc}\hline
HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   & r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\sigma_{LOS}\)& \(l_T\)* & \(Re\)*& - \\
Region    &  [km/s] &  [pc]    &        & [pc] &      &[km/s]& [pc] & &  \\ \hline
NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  & 27   & 14.7 & 7.69 &  5.1 & &  \\
NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) & 20   & 21.4 & 5.74 & 4.4  & &  \\
Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0..09}\)  & 12   & 19.9 &      & 1.56 & &  \\ 
Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) & 15   & 22.1 &      & 1.95 & &  \\   
30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) & 11   & 8.9  &      & 0.69 & &  \\
Carina    &  4.22    &   0.55    &    1   & 2    & 16.1 & 2.7  &      & &  \\
NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &     &     &     &  & &  \\
Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.36\(^{+0.04}_{-0.03}\) &  6   & 10.1 &      &      & &  \\ 
Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &  -   & 27.6 &   6  &      & &  \\
Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &     &  &  6   &      &  & \\

\end{tabular}\label{tab:Res}
\end{center}
\end{table*}

\subsection{Plane of sky radial velocity dispersion \(\sigma\)}

The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\).
NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
With the lowest values is Hubble V with 2.8 km s\(^{-1}\) and Lagoon with 2.7 km s\(^{-1}\).

The index \(m\) seems biased to \(m>\)1.6 for the extragalactic regions and \(m\sim\)1 for nearby regions.
This could be attributed to a data quality issue since we are not able to resolve distant regions in the same way we do with nearby objects.
Since we are not observing all the inertial range on distant regions \(m\) should be taken a secondary parameter.

We can compute the m$_{3D}$ index from m$_{2D}$ ($m$ till now) if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution following the procedure by \cite{arthur2016turbulence}.
This can be assumed throughout the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
For our observations we have 0.9 $<$ m$_{3D}$ $<$ 1.95.

Ideally the correlation length, \(r_0\), should represent the scale of dominant energy injection. 
Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
The possibility the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
The range covered our results goes from 0.07 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  We apply the technique to archival \halpha\ observations of a diverse sample of 9 \hii{} regions
  in the Milky Way and other Local Group galaxies,
  which span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form to the second-order velocity structure function,
  we extract three parameters for the fluctuations in each region:
  total velocity dispersion, \(\sigma\),
  autocorrelation length, \(r_0\), and power-law slope, \(m\).
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

\definecolor{WillCommentColor}{rgb}{0.6,0.11,0.4}
\newcommand\WILL[1]{\textbf{\color{WillCommentColor}#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}
\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.

@@

The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.

The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

\begin{table*}
\begin{center}\caption{Sumary of properties \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}}
\begin{tabular}{ccccccccc}\hline
HII    &  Dist.  & Diameter & log L(H$_{\alpha}$) & SFR      &  $ \langle N_{e} \rangle_{rms}$    & M(H$^{+}$) & Filling & \(\sigma_{W}\) \\
Region     &  [kpc] &  [pc]     &  [erg/s]            & [ ]      & [cm$^{-3}$] & [M$_{\odot}$] & Factor & [km/s] \\ \hline
NGC 604   &   840  & 400     &    39.65     & 0.011    & 3  & 7 $\times$ 10$^{5}$ & 0.1 & 23.1 \\
NGC 595   &   840  & 400     &    39.36     & 0.009    & 4  & 4.6 $\times$ 10$^{5}$ & & 27.1 \\
Hubble X  &   500  & 160     &    38.6      &  0.004   &  5 & 23 000& 0.02 & 13.4 \\
Hubble V  &   500  & 130     &    38.87     &  0.005   &  8 &    & & 14.7 \\
30 Dor    &   50   & 98.9    &    39.76     & 0.0130   & 250&    & & 31.7 \\
Carina    &   2.35 & 15      &    39.6      & 0.01     & 500&    & 0.05 & \\
NGC 346   &   61.7 & 64      &    38.67     & 0.0021   & 100&    &     & \\
Lagoon    &   1.25 & 25      &    37.47     & 0.0001   &  60& 900& 0.012 & \\
Orion     &   0.4  & 5       &    37        & 0.000053 & 150& 50 & 0.027 & \\\hline
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

\subsection{Regions in M33 and NGC 6822}

@@

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
This follows if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
In these sense the structure function is used as a tool to investigate the projection of a three.dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

@@

where $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1984ApJ...277..556S,arthur2016turbulence}.
The term $r_{0}$ is the correlation length of the turbulence, the value of \(r\) in pc where equation \ref{eq:S} reach the value of \(\sigma^2\), and $m$ is the index that adjust our results.
The term $\zeta$ is a correction for small scales considering a Gaussian seeing, $s_{0}$, and has the form $tanh^{2}[(r/2s_{0})^2]$, and \(\eta\) is the observational noise. 
In this idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}.

\subsection{Application to our HII regions sample}

The results and the errors of $r_{0}$ and $m$ are obtained using equations \ref{eq:S} and \ref{eq:b} in a chi-square (\(\chi^2)\) statistic in order to do a non-linear least-squares fit of a model to our data \citep{newville_matthew_2014_11813}. 
In this way we avoid one fundamental problem in the interpretation of the structure function results. The slope in the majority of previous studies and hence, the correlation length, is obtained by eye. 
The traditional way to find it is to determine a particular range of ascending values in the structure function results. 
If this increase in values is stopped it is commonly assumed that one particular range has been found. 
In some cases this procedure keeps going up to large scales, giving two or more inertial regimes;this has lead to the interpretation of multiple energy injection scales.
Since the previous described method isn't conclusive we choose the chi-square (\(\chi^2)\) statistic to present the significance of our results. 
This way we can maintain consistency in our analysis.

@@

\begin{table*}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..347H}
      g) \citet{arthur2016turbulence}.
    } 
\begin{tabular}{cccccc}\hline
HII         &$\mu$   &$\sigma^{2}$       &No. of  &\(s_0\)* & Previously \\
Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  &[pc]     & used in:   \\ \hline
NGC 604     &3.56    &54.63              &9 510   &1.73     &a,b         \\
NGC 595     &2.82    &44.13              &8 765   &1.73     &-           \\
Hubble V    &-1.23   &7.87               &5 832   &1.02     &-           \\
Hubble X    &-5.95   &12.9               &6 925   &1.02     &-           \\
30Dor       &265.56* &252.79             &363 059 &0.2      &c           \\
Carina      &-8.83   &17.89              &855     &         &d           \\
NGC 346     &        &31.36              &112 796 &         &            \\
Lagoon      &-6.26   &7.53               &1 176   &         &e           \\
Orion Large &-1.25   &10.43              &359     &         &f           \\
Orion Small &        &9.61               &        &         &g            \\ \hline
\end{tabular}\label{tab:Data}
\end{center}
\end{table*}

@@

Table \ref{tab:Res} presents the three parameters we obtain from the analysis on the fluctuations of the velocities using the second order structure function.
The second column is the velocity dispersion \(\sigma\) of each sample of centroid velocities.
The third column is the correlation length \(r_0\).
The index \(m\) is shown in the forth column;
this index is used as a reference for comparison between theory and observations.
In the fifth column we show the reduced chi-square value obtained using a non-linear regression algorithm. 
Finally we show the mean velocity dispersion across the line-of-sight \(\sigma_{LOS}\) with the aim to investigate how statistically homogeneous the regions are.

%In the appendix \ref{sec:StructFunct} the Figures \ref{fig:SF604}-\ref{fig:SFM42} show the second-order structure functions of the different HII regions for the \halpha\ emission line.

The power-law fit in the structure function for the both regions in the M33 galaxy in is performed above scales of 1.7 pc.
For NGC 604 the index is correspond to 1.95 with a correlation length of 8.75 pc. For NGC 595 the values obtained are 1.75 and 9 pc.
For NGC 6822 regions, Hubble X and Hubble V, the $m$ index is 1.7 and 1.62, with a correlation length of 3.62 and 2.7 pc, respectively.
The 30Dor nebula \citep{Castro:2018a} has a correlation length of 2.7 pc and an index of 1.22.
NGC 346 correlation length is 1.4 pc and its index is 1.13.

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}. It is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}, we use this combined sample for the structure function analysis.
Carina has an index of 0.82 with a correlation length of 0.94 pc.
The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.78 pc and a index of 1.56.

For Orion we have the opportunity to study two different observations. \citet{1987A&A...176..347H} observations allow us to study the large scale of the nebula, covering 4 pc, while \cite{arthur2016turbulence} allow us to study the small scales up to 0.4 pc. Large scales results shows an index of 0.9 with a correlation length of 0.84 pc while the small scales have 1.44 and 0.062 pc.

\begin{table*}
\begin{center}\caption{Main results.}
\begin{tabular}{ccccccccc}\hline
HII         &\(\sigma\) &\(r_0\)                     &\(m\)   &Reduced &\(\langle \sigma_{LOS} \rangle \) \\
Region      &[km/s]     &[pc]                        &                           &chi-square &  [km/s]\\ \hline
NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &0.81 &16.2  \\
NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &0.47 &18.3  \\
Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &0.19 &13.4  \\ 
Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &0.13 &12.3  \\   
30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &0.49 &31.7* \\
Carina      &4.22       &0.94\(^{+0.94}_{-0.13}\)    &0.82\(^{+0.08}_{ -0.08}\)  &0.39 &22.4   \\
NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &0.34 &  \\
Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &0.59 &13.6     \\ 
Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &0.27 &6  \\
Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &0.64 &6 \\\hline	  
\end{tabular}\label{tab:Res}
\end{center}
\end{table*}

%\begin{table*}
%\begin{center}\caption{Main results.}
%\begin{tabular}{ccccccccccc}\hline
%HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   &Reduced& r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\langle \sigma_{LOS} \rangle \) & \(l_T\)* & \(Re\)*& - \\
%Region    &  [km/s] &  [pc]    &&   chi-square     & [pc] &      &[km/s]& [pc] & &  \\ \hline
%NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  &0.81& 27   & 14.7 & 16.2 &  5.1 & &  \\
%NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) &0.47& 20   & 21.4 & 18.3 & 4.4  & &  \\
%Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0.09}\)  & 0.19& 12   & 19.9 &  13.4    & 1.56 & &  \\ 
%Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) &0.13& 15   & 22.1 &  12.3    & 1.95 & &  \\   
%30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) &0.49& 11   & 8.9  &      & 0.69 & &  \\
%Carina    &  4.22    &    0.94\(^{+0.94}_{-0.13}\)     &    0.82\(^{+0.08}_{ -0.08}\)   &0.39& 2    & 16.1 & 22.4  &      & &  \\
%NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &0.34&     &     &     &  & &  \\
%Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.56\(^{+0.05}_{-0.05}\) &0.59&  6   & 10.1 &  13.6    &      & &  \\ 
%Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &0.27&  -   & 27.6 &   6  &      & &  \\
%Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &0.64&     &  &  6   &      &  & \\	  
%\end{tabular}\label{tab:Res}
%\end{center}
%\end{table*}

%\subsection{Plane of sky radial velocity dispersion \(\sigma\)}

The highest \(\sigma\) is 15.8 km s\(^{-1}\) for 30Dor.
This is two times higher than NGC 604 that has a value of 7.4 km s\(^{-1}\), followed by NGC 595 with 6.64 km s\(^{-1}\).
NGC 346 is next with a value of 5.6 km s\(^{-1}\), followed by Carina with 4.22 km s\(^{-1}\).
Hubble X and M42 have a value of 3.59 and 3.23 km s\(^{-1}\), respectively.
Hubble V has 2.8 km s\(^{-1}\) and last mof all sample is Lagoon with 2.7 km s\(^{-1}\).

It is possible that the index \(m\) is biased to \(m>\)1.6 for the extragalactic regions and \(m<\)1.5 for nearby regions.
This could be attributed to a data quality issues because the inability to resolve distant regions in the same way we do with nearby objects.
Since we are not observing all the inertial range on distant regions the \(m\) parameter  should be taken with some caution.

We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
For our observations we have 0.82 $<$ m$_{3D}$ $<$ 1.95.
This is done following the procedure by \cite{arthur2016turbulence} assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$.
This give us a considerable large range of 1. 
Though \cite{arthur2016turbulence} are comparing emission lines and not regions we can conclude that the index \(m\) still is far away as a unique parameter for measuring turbulence and that the three-dimensional behavior would probably encompass a wide range of indices as seen in the two-dimensional observations.

Ideally the correlation length \(r_0\), should represent the scale of dominant energy injection. 
Since it is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates, it is difficult to pinpoint one particular as main responsible. 
The possibility that the correlation length reveals the answer to the cause of observed motions is a long shot, but it is clear that each velocity field has a corresponding \(r_0\) value. 
The range covered in our results goes from 0.06 to 9 pc, a small range in comparison with the two order magnitude difference in size and luminosity.

\subsection{Other significant scales}

In the Table \ref{tab:ResII} the second column show the separation where the value 2\(\sigma\) is reached.
We also show the ratio \(r_{max}/r_{0}\), where \(r_{max}\) is the maximum separation or lag in pc; this value is related to the size of each sample box. 
The forth column shows the Taylor scale, \(l_T\), which measures the average spatial extent of velocity gradients. \citet{1999ApJ...524..895M} define this scale as:

@@

where \(r_s\) is the smallest separation \(r\) and \(\sigma_{r_s}\) the value of the structure function at that separation.

It is possible to calculate how this Taylor micro-scale is related to the correlation length by:

@@

Finally in te table we present the Reynolds Number...

\begin{table}
\begin{center}\caption{Scales...}
\begin{tabular}{cccccc}\hline
HII         &r$_{2\sigma}$ &\(r_{max}\)/\(r_0\)  &\(l_T\) & \(Re\)* \\
Region      &[pc]          &                     &[pc]    &   \\ \hline
NGC 604     &28.73         &15.49                &5.35    &   \\
NGC 595     &18.50         &21.01                &5.57    &   \\
Hubble V    &11.61         &19.95                &1.80    &   \\ 
Hubble X    &21.99         &21.67                &1.97    &   \\   
30 Dor      &11.26         &8.99                 &0.59    &   \\
Carina      &1.93          &31.55                &0.402   &   \\
NGC 346     &5.78          &10.73                &0.39    &   \\
Lagoon      &6.14          &10.68                &0.66    &   \\ 
Orion Large &-             &2.98                 &0.24    &   \\
Orion Small &0.162         &10.42                &0.019   &   \\ \hline	  
\end{tabular}\label{tab:ResII}
\end{center}
\end{table}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\subsection{Scaling relations}
\subsection{Correlations between physical properties and turbulent parameters}

As we mentioned in the introduction, the scaling relations between parameters like size and luminosity are common tools to study HII regions along dwarf galaxies and high-redshift star formation regions; in the past those relationships, particularly in GEHRs, made them candidates as standard candles. 
We apply these methods with the turbulent parameters \(r_0\) and index \(m\).

Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$. Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96. 
By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of 6.57 10\(^{-6}\).
Applying and ordinary least-square regression we find a form Y = aX + b; this values laong the previous ones y shown in Table \ref{tab:RestStats}.

The relationship between L vs \(\sigma\) is one of the most studied. This relationship help us understanding how the star formation affects the gas motions and how star formation is regulated by feedback processes. Figure \ref{fig:sigvsl} shows different studies of the L vs \(\sigma\) relationship. In this case it is normally used the deconvolution of the observed lines taking account thermal broadening and instrumental broadening leaving the \(\sigma_{LOS}\).
